Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex

Given a set a $d$-dimensional feature vectors $x_l^u\in X_u$, $l=[1,2,\ldots,L]$, extracted from the scene $s_u$, $u=[1,2,\ldots,U]$, the goal of KMeans is to partition $X_u$ into $M$ clusters $c^u_m\in C_u$, $m=[1,2,\ldots,M]$. The partitioning is done by minimizing for each $m$ cluster the squared error between its empirical mean (centroid) and the points it contains. Given $\mu_m^u$ the centroid of the cluster $c_m^u$, KMeans minimizes the following objective function:

>>>>

Given a set of $d$-dimensional feature vectors $x_l^u\in X_u$, $l=[1,2,\ldots,L]$, extracted from the scene $s_u$, $u=[1,2,\ldots,U]$, the goal of KMeans is to partition $X_u$ into $M$ clusters $c^u_m\in C_u$, $m=[1,2,\ldots,M]$. The partitioning is done by minimizing for each $m$ cluster the squared error between its empirical mean (centroid) and the points it contains. Given $\mu_m^u$ the centroid of the cluster $c_m^u$, KMeans minimizes the following objective function:
